I/O simulation model with Linux page cache, integration and evaluation in SimGrid framework

### 2020-06-15 paper_io_sim.tex
Edits in Algo 1

\author{\IEEEauthorblockN{Hoang-Dung Do, Tristan Glatard and Val\'erie Hayot-Sasson
  }\\
  \IEEEauthorblockA{
    Department of Computer Science and Software Engineering, Concordia University, Montreal, Canada
  }
}

@@

			\begin{algorithm}\caption{File read simulation}\label{alg:read}
				\small
				\begin{algorithmic}[1]
					\Input
        				\Desc{fn}{file name}
        				\Desc{fs}{file size}
						\Desc{rt}{current simulated run time}
						\Desc{mm}{MemoryManager object}
						\Desc{$r_m$}{memory read bandwidth}
						\Desc{$r_d$}{disk read bandwidth}
   					\EndInput
   					\Output
						\Desc{rt}{simulated run time after the file is read}
   					\EndOutput
					\State req = max(0, 2 * fs - mm.cached(fn) - mm.avail\_mem) 
					\State avail = max(0, 2 * fs - mm.cached(fn) - mm.dirty)
					\State rt = rt + mm.flush(req - avail)	
					\State req = max(0, 2 * fs - mm.cached(fn) - mm.free\_mem)
					\State mm.evict(req) 
					\If {mm.cached(fn) $>$ 0}  \Comment{Read file cached data}
    					\State mm.cache\_read(fn) 
						\If {mm.cached(fn) == fs} \Comment{If all file data is cached}
    						\State time = mm.cached(fn) / $r_m$
    						\State mm.periodic\_flush(time) 
							\State rt = rt + time
						\EndIf
					\EndIf
					\If {mm.cached(fn) $<$ fs} \Comment{Read uncached data from disk}
						\State mm.disk\_read(fs - mm.cached(fn), fn)
    					\State rt = rt + (fs - mm.cached(fn)) / $r_d$
					\EndIf

>>>>

\author{\IEEEauthorblockN{Hoang-Dung Do, Val\'erie Hayot-Sasson, Tristan Glatard
  }\\
  \IEEEauthorblockA{
    Department of Computer Science and Software Engineering, Concordia University, Montreal, Canada
  }
}

@@

			\begin{algorithm}\caption{File read simulation}\label{alg:read}
				\small
				\begin{algorithmic}[1]
					\Input
        				\Desc{fn}{file name}
        				\Desc{fs}{file size (assumed to fit in memory)}
						\Desc{rt}{current simulated run time}
						\Desc{mm}{MemoryManager object}
						\Desc{$r_m$}{memory read bandwidth}
						\Desc{$r_d$}{disk read bandwidth}
   					\EndInput
   					\Output
						\Desc{rt}{simulated run time after the file is read}
   					\EndOutput
					\State rt = rt + mm.flush(2*fs - mm.cached(fn) - mm.avail\_mem)
					\State mm.evict(2*fs - mm.cached(fn) - mm.free\_mem) 
					\If {mm.cached(fn) $>$ 0}  \Comment{Read file cached data}
    					\State mm.cache\_read(fn) 
						\State rt = rt + mm.cached(fn) / $r_m$
					\EndIf
					\If {mm.cached(fn) $<$ fs} \Comment{Read uncached data from disk}
						\State mm.disk\_read(fs - mm.cached(fn), fn)
    					\State rt = rt + (fs - mm.cached(fn)) / $r_d$
					\EndIf
